---
title: "First Pass DDS 1"
author: "Adam Canton & Carl Keusseyan"
date: "6/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(magrittr)
library(dplyr)
library(tidyr)
library(forcats)
library(matrixStats)
library(GGally)
library(caret)
library(corrplot)
library(cowplot)
library(ggExtra)
library(ggthemes)
library(maps)
library(usmap)
library(naniar)
library(olsrr)
library(stringr)
library(e1071)
library(FNN)
library(MASS)
library(ggthemes)
library(caret)
library(e1071)
library(reshape2)
library(RANN)
```

```{r}
# pulling datasets
Beers <- read.csv(file.choose())
Breweries <- read.csv(file.choose())

# Merge Beer and Brewery 
BeerBrewery = merge(Beers, Breweries, by.x = "Brewery_id", by.y = "Brew_ID")

# Change some column names for tidyness
names(BeerBrewery)[2] <- "Beer"
names(BeerBrewery)[8] <- "Brewery"

```

```{r}
# Part of question 3 - Imputing some researched values for ABV and IBU - Intializing  ---- 
# Filled in researched Data and Intialize Data sets

## 75 Brewery Vivant Fat Paczki - 7.5%
BeerBrewery$ABV[75] = 0.075
## 76 Brewery Vivant Earth-Like-Planets 5.5%
BeerBrewery$ABV[76] = 0.055
## 186 Sun King Brewing Company 30 Min Coma 4.5% abv - 65 IBU
BeerBrewery$ABV[186] = 0.045
BeerBrewery$IBU[186] = 65
## 193 Sun King Brewing Company Bourbon Barrel Cowbell 6% abv - 23 IBU
BeerBrewery$ABV[193] = 0.060
BeerBrewery$IBU[193] = 23
## 227 Cedar Creek Brewery Special Release - Actually refers to two separate beers
## 252 James Page Brewing Company Bastian 6.2% no IBU
BeerBrewery$ABV[252] = 0.062
## 440 Crazy Mountain Brewing Company Winter Wondergrass Festival Ale 4.9% no IBU
BeerBrewery$ABV[440] = 0.049
## 441 Crazy Mountain Brewing Company Boohai Red Ale 6%
BeerBrewery$ABV[441] = 0.060
## 508 Blue Owl Brewing Professor Black 6.2%
BeerBrewery$ABV[508] = 0.062
## 509 Blue Owl Brewing Little Boss 3.8%  - 7 IBU
BeerBrewery$ABV[509] = 0.038
BeerBrewery$IBU[509] = 7
## 510 Blue Owl Brewing Van Dayum! 5.7%
BeerBrewery$ABV[510] = 0.057
## 511 Blue Owl Brewing Spirit Animal 5.5%
BeerBrewery$ABV[511] = 0.055
## 568 Keweenaw Brewing Company U. P. Witbier 5.5% No IBU
BeerBrewery$ABV[568] = 0.055
## 569 Keweenaw Brewing Company November Gale Pale Ale 5% - 5 IBU
BeerBrewery$ABV[569] = 0.050
BeerBrewery$IBU[569] = 5
## 570 Keweenaw Brewing Company Olde Ore Dock Scottish Ale 7%
BeerBrewery$ABV[570] = 0.070
## 571 Keweenaw Brewing Company Widow Maker Black Ale 5.2%
BeerBrewery$ABV[571] = 0.052
## 572 Keweenaw Brewing Company Lift Bridge Brown Ale 5%
BeerBrewery$ABV[572] = 0.050
## 573 Keweenaw Brewing Company Pick Axe Blonde Ale 4.9%
BeerBrewery$ABV[573] = 0.049
## 574 Keweenaw Brewing Company Red Jack Amber Ale 5.1%
BeerBrewery$ABV[574] = 0.051
## 629 West Sixth Brewing West Sixth IPA 7%
BeerBrewery$ABV[629] = 0.07
## 789 Weston Brewing Company Royal Lager Couldnt Find
## 791 Weston Brewing Company O'Malley's Stout 5.5%
BeerBrewery$ABV[791] = 0.055
## 793 Weston Brewing Company O'Malley's Cream Ale 0% ?
## 900 Fort Pitt Brewing Company Fort Pit Ale Couldnt find - not in production any longer
## 992 Oskar Blues Brewery The Crowler - not an actual beer
## 993 Oskar Blues Brewery Cand Aid - not an actual beer
## 994 Oskar Blues Brewery Icey P.A. 7% 
BeerBrewery$ABV[994] = 0.07
## 996 Oskar Blues Brewery Birth IPA couldnt find
## 1158 Capital Brewery Supper Club Lager 5.2% 
BeerBrewery$ABV[1158] = 0.052
## 1298 Rochester Mills Brewing Company Cal and Co Black Cherry Porter 7%
BeerBrewery$ABV[1298] = 0.07
## 1424 Ska Brewing Company Autumnal Mole' Stout 5.8%
BeerBrewery$ABV[1424] = 0.058
## 1480 Thunderhead Brewing Company Cornstalker Dark Wheat 5.2% 
BeerBrewery$ABV[1480] = 0.052
## 1631 Iron Hill Brewery & Restaurant Appreciation Ale 9.4%
BeerBrewery$ABV[1631] = 0.094
## 1887 Blue Blood Brewing Company Double Play Pilsner 5.2%
BeerBrewery$ABV[1887] = 0.052
## 1892 Blue Blood Brewing Company N Street Drive-In 50th Anniversary IPA 8.6%
BeerBrewery$ABV[1892] = 0.086
## 1919 Revolution Brewing Rye Porter No longer in production
## 1924 Revolution Brewing Miner's Gold 5.1%
BeerBrewery$ABV[1924] = 0.051
## 1951 Santa Fe Brewing Company Sante fe Oktoberfest 6%
BeerBrewery$ABV[1951] = 0.06
## 2096 MillKing It Productions AXL Pale Ale 5.2
BeerBrewery$ABV[2096] = 0.062
## 2177 Brindle Dog Brewing Company Tampa Pale Ale 6.2
BeerBrewery$ABV[2177] = 0.062
## 2178 Brindle Dog Brewing Company Orange Grove Wheat Ale - couldnt find
## 2184 Pete's Brewing Company Pete's Wicked Pale Ale (1997) 5.3
BeerBrewery$ABV[2184] = 0.053
## 2227 The Manhattan Brewing Company Manhattan Gold Lager (1990) 5.2 (Beer Authority NYC)
BeerBrewery$ABV[2227] = 0.052
## 2234 Dock Street Brewery Dock Street Amber Beer (1992) 5%
BeerBrewery$ABV[2234] = 0.05
## 2242 Devil's Canyon Brewery Kaleidoscope Collaboration (2012) 5.5
BeerBrewery$ABV[2242] = 0.055
## 2259 Cans Bar and Canteen THP White (2006) Closed
## 2260 Cans Bar and Canteen THP Amber (2006) Closed
## 2261 Cans Bar and Canteen THP Light (2006) Closed
## 2262 Cans Bar and Canteen THP Dark (2006) Closed
## 2296 Spilker Ales Hopluia (2004) 5.2
BeerBrewery$ABV[2296] = 0.052
## 2323 Scotty K NA is a non-alcoholic beer that has no IBU.
BeerBrewery$IBU[2323] = 1
## 2345 Buckbean Brewing Company Roler Bock 7.2
BeerBrewery$ABV[2345] = 0.072
## 2351 Dolores River Brewery Dolores River Hefeweizen No Info
## 2352 Dolores River Brewery Dolores River ESB 6.1
BeerBrewery$ABV[2352] = 0.061
## 2353 Dolores River Brewery Snaggletooth Double Pale Ale No Info 
## 2354 Dolores River Brewery Dolores River Pale Ale 5.8
BeerBrewery$ABV[2354] = 0.058
## 2355 Dolores River Brewery Dolores River Dry Stout No info
## 2356 Dolores River Brewery Dolores River Mild No info
## 2357 Flat Rock Brewing Company Inclined Plane Ale 4.2
BeerBrewery$ABV[2357] = 0.042
## 2365 Harvest Moon Brewing Company Great Falls Select Pale Ale 5
BeerBrewery$ABV[2365] = 0.05
## 2370 Grand Canyon Brewing Company Black Iron India Pale Ale 7.2
BeerBrewery$ABV[2370] = 0.072
## 2394 Prescott Brewing Company Ponderosa IPA 6.5 70
BeerBrewery$ABV[2394] = 0.065
BeerBrewery$IBU[2394] = 70
## 2395 Prescott Brewing Company Liquid Amber Ale 5 17
BeerBrewery$ABV[2395] = 0.050
BeerBrewery$IBU[2395] = 17


# adds a factorized version of IBU to the data set and displays the levels - 108 of them including NA
BeerBrewery$IBUFac = as.factor(BeerBrewery$IBU)
BeerBrewery$IBUFac = addNA(BeerBrewery$IBUFac)
#levels(BeerBrewery$IBUFac)

# Creates ABV Factor based on popular perception of ABV strength: Weak - Abv(0<0.04), Normal - Abv(0.04<= 0.07), Strong - Abv(>0.07)
ABVFac = cut(BeerBrewery$ABV, breaks = c(0,0.04,0.07,0.15), labels = c("Weak ( < 0.04)", "Normal (0.04 - 0.07)", "Strong ( >7)"))
BeerBrewery = cbind(BeerBrewery,ABVFac)

# Creates a Data set that mirrors the original but with NA's deleted
BeerBreweryNA.delete = BeerBrewery %>% filter(IBU != "NA")

# removes Beers df, it is not used again after this point
rm(Beers)
```

```{r, warning=FALSE}
# This is analysis question 1 - Breweries by State ----
# Show number of breweries by state
Breweries %>% group_by(State) %>% count_() %>% ggplot(aes(x = reorder(State, -n), y = n )) +
  geom_col() + theme(axis.text.x = element_text(angle = 90, vjust = -0.05)) +  xlab("State") + ylab('Number of Breweries') + 
  ggtitle("Number of Breweries by State") + geom_text(aes(label = n), vjust = -0.5, size = 3)

# Geographical Map
mapBreweries = Breweries %>% group_by(State) %>% count_()
mapBreweries$State = as.character(mapBreweries$State)
mapBreweries$State = sub(" ", "", mapBreweries$State)
map2 = merge(statepop, mapBreweries, by.x = "abbr", by.y = "State")
plot_usmap(data = map2, values = "n", color = "red", labels = TRUE, label_color = "white") + 
  scale_fill_continuous(name = "Brewery count", label = scales::comma) + 
  labs(title = "USA MAP", subtitle="Brewery counts by State") +
  theme(legend.position = "right")
```

```{r}
# This is analysis question 2 - The first and last 6 observations ----
head(BeerBrewery, 6)
tail(BeerBrewery, 6)
```

```{r}
# Part of Question 3 - Looking at whats missing ----
gg_miss_var(BeerBrewery)

na_count <- sapply(BeerBrewery, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)
na_count
```

```{r}
# Not part of a specific question - Shows IBU with and without its NAs ----
# Shows IBU with and Without the NA - Full Set
BeerBrewery %>% group_by(IBUFac) %>% filter(IBU != "NA") %>% summarise(countibu = n()) %>% ggplot(aes(x = IBUFac, y = countibu)) +
  geom_col(width = 0.75) + xlab("IBU Factor") + ylab("# of Beers with this IBU") + theme(axis.text.x = element_text(angle = 90, vjust = -0.05))

BeerBrewery %>% group_by(IBUFac) %>% summarise(countibu = n()) %>% ggplot(aes(x = IBUFac, y = countibu)) +
  geom_col(width = 0.75) + xlab("IBU Factor") + ylab("# of Beers with this IBU") + theme(axis.text.x = element_text(angle = 90, vjust = -0.05))

# Same as above but only top 15
BeerBrewery %>% group_by(IBUFac) %>% filter(IBU != "NA") %>% summarise(countibu = n()) %>%
  arrange(-countibu) %>% slice(1:15)  %>% ggplot(aes(x = reorder(IBUFac, countibu), y = countibu)) +
  geom_col(width = 0.75) + xlab("IBU Factor") + ylab("# of Beers with this IBU") + coord_flip()
  theme(axis.text.x = element_text(angle = 90, vjust = -0.05))

BeerBrewery %>% group_by(IBUFac) %>% summarise(countibu = n()) %>% arrange(-countibu) %>% slice(1:15) %>%
  ggplot(aes(x = reorder(IBUFac, countibu), y = countibu)) + geom_col(width = 0.75) + xlab("IBU Factor") + ylab("# of Beers with this IBU") +
  coord_flip() + theme(axis.text.x = element_text(angle = 90, vjust = -0.05))
```

```{r}
# not part of a specfic question - Display top 15 beer styles ----
# Display top 15 Styles by count
BeerBrewery %>% group_by(Style) %>% summarise(CountStyle = n()) %>% arrange(-CountStyle) %>% slice(1:15) %>%
  ggplot(aes(x = reorder(Style, CountStyle), y = CountStyle)) + geom_col() +
  theme(axis.text.x = element_text(angle = 90, vjust = -0.05)) + ylab("Number of Beers") + xlab("Most Popular Styles") + coord_flip() + 
  ggtitle("15 Most Popular Beer Styles by Style Frequency")
```

```{r, warning=FALSE}
# Not part of a specific question - Looking at ABV by factor ---- 
BeerBrewery %>% group_by(ABVFac) %>% summarise(CountABVFac = n()) %>% na.omit() %>%
  ggplot(aes(x = ABVFac, y = CountABVFac)) + geom_col(width = 0.75) + geom_text(aes(label = CountABVFac), vjust = -0.3, size = 4) + 
  xlab("ABV Category") + ylab("Frequency") + ggtitle("Number of Beers by ABV Factor")
```

Need to look at ABV Distribution - looks approximately normal with a small right skew - QQplot indicates we might be able to log variable
```{r, warning=FALSE}
# Analysis of number 6 - Summary Stats and distribution of ABV ----
# If we take off the meaningless y axis stuff from the boxplot it un-centers it from the histogram - better to have it on center? Currently on
g1 = BeerBrewery %>% ggplot(aes(x = ABV)) + geom_histogram(binwidth = 0.0025) + xlim(0,0.125) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank())

g2 = BeerBrewery %>% ggplot(aes(x = ABV)) + geom_boxplot() + xlim(0,0.125) + theme(axis.ticks.y = element_blank())

g3 = BeerBrewery %>% ggplot(aes(sample = ABV)) + stat_qq_line() + stat_qq() + ylim(0,0.125) + xlab("Quantile") + ylab("ABV")

g4 = ggdraw() + draw_label("Distribution Characteristics \nof ABV", color = "Gray2", size = 20)

plot_grid(g1,g3,g2,g4, ncol = 2)
```

```{r}
# IBU Distribution Characteristics - Summary Stats and distribution of IBU before impute (q3) ----
g1 = BeerBrewery %>% na.omit() %>% ggplot(aes(x = IBU)) + geom_histogram(binwidth = 2) + xlim(0,150) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank())

g2 = BeerBrewery %>% na.omit()  %>% ggplot(aes(x = IBU)) + geom_boxplot() + xlim(0,150) + 
  theme(axis.ticks.y = element_blank())

g3 = BeerBrewery %>% na.omit() %>% ggplot(aes(sample = IBU)) + stat_qq_line() + stat_qq() + ylim(0,150) + xlab("Quantile") + ylab("IBU")

g4 = ggdraw() + draw_label("Distribution Characteristics \nof IBU\n (Before Impute)", color = "Gray2", size = 20)

plot_grid(g1,g3,g2,g4, ncol = 2)
```
The scatterplot below shows the we will likely have especially bad predictions when ABV > 0.1 or less than ~ 0.025
```{r, warning=FALSE}
# Part of Number 7 - Scatterplot of IBU v ABV ----
BeerBrewery %>% na.omit() %>% ggplot(aes(x = ABV, y = IBU, color = ABVFac)) + geom_point() + geom_smooth(formula = y~x) + xlim(0,0.15) + geom_jitter() + 
  ggtitle("Scatterplot of IBU v ABV") + labs(color = "ABV by Strength")
```
# Start of Linear models. These are to look at imputing by using LM predictions
```{r}
# Part of question 3 - Set Seed and Train/test sets ----  
set.seed(4)
splitperc = 0.70
index<- sample(1:dim(BeerBreweryNA.delete)[1],round(splitperc*dim(BeerBreweryNA.delete)[1]),replace=F)
train<- BeerBreweryNA.delete[index,]
test<- BeerBreweryNA.delete[-index,]
```

```{r}
# Simple model - linear model 1 and fit stats (q3) -  IBU ~ ABV ----
linearmodel1 <- lm(IBU ~ ABV, data = train)
summary(linearmodel1)
ols_plot_resid_fit(linearmodel1)
ols_plot_resid_lev(linearmodel1)
ols_plot_resid_qq(linearmodel1)
ols_plot_resid_hist(linearmodel1)
ols_plot_cooksd_bar(linearmodel1)
```

Whats with point 729???
```{r}
# Complex Model - Linear model 2 and fit stats(q3) - IBU ~ log(ABV)^3 ----
linearmodel2 <- lm(IBU ~ poly(log(ABV),3), data = train)
summary(linearmodel2)
ols_plot_resid_fit(linearmodel2)
ols_plot_resid_lev(linearmodel2)
ols_plot_resid_qq(linearmodel2)
ols_plot_resid_hist(linearmodel2)
ols_plot_cooksd_bar(linearmodel2)
```

There is some serious correlation in the above residual plots which is a bit troubling. This would suggest we need a correction of some sort or more predictors (of which we have none). Logging the response does not help. Model 2 gets rid of a lot of the correlation - but adds a non-constant variance violation, which again is not alleviated by log transforms.

All this leads me to think we may want a non-parametric model. So KNN or NB

```{r}
# Linear Model Benchmarking (q3) ----
iterations = 500
splitperc = 0.70
# column building
LModelRMSE1 = c()
LModelRMSE2 = c()


for(i in 1:iterations)
{
  #set.seed(i)
  index<- sample(1:dim(BeerBreweryNA.delete)[1],round(splitperc*dim(BeerBreweryNA.delete)[1]),replace=F)
  train<- BeerBreweryNA.delete[index,]
  test<- BeerBreweryNA.delete[-index,]
  
  predictions1 <- linearmodel1 %>% predict(test)
  
  d1 = data.frame(R2 = R2(predictions1,test$IBU), RMSE = RMSE(predictions1,test$IBU), MAE = MAE(predictions1, test$IBU))
  LModelRMSE1 = c(LModelRMSE1,d1$RMSE)
  
  predictions2 <- linearmodel2 %>% predict(test)

  d2 = data.frame(R2 = R2(predictions2,test$IBU), RMSE = RMSE(predictions2,test$IBU), MAE = MAE(predictions2, test$IBU))
  LModelRMSE2 = c(LModelRMSE2, d2$RMSE)
  
}  
  
Linear.Model.Average.RMSE = cbind(LModelRMSE1, LModelRMSE2)
linearRmsedf = as.data.frame(Linear.Model.Average.RMSE)
Means = colMeans(Linear.Model.Average.RMSE)
SDs = round(colSds(Linear.Model.Average.RMSE), 5)
range1 = max(linearRmsedf$LModelRMSE1) - min(linearRmsedf$LModelRMSE1)
range2 = max(linearRmsedf$LModelRMSE2) - min(linearRmsedf$LModelRMSE2)
linearRmsedf = melt(linearRmsedf)
  
  
# Looking at descriptive stats
Means
print("Standard Devs")
SDs
print("ranges - measure of variance between train/test shuffles")
print(paste("Model 1 Range" , round(range1, 5)))
print(paste("Model 2 Range" , round(range2, 5)))
cat("Summary: 
    ")
summary(Linear.Model.Average.RMSE)

# Scatter
Pred1 <- data.frame(Value = predictions1, Model = "Linear Model 1")
Pred2 <- data.frame(Value = predictions2, Model = "Linear Model 2")
PredActual <- data.frame(ActualValue = test$IBU)
PredAll <- rbind(Pred1, Pred2)
PredActual <- rbind(PredActual,PredActual)
PredAll <- cbind(PredAll, PredActual)

#Are the fits shown here a bit misleading compared to their equations? I think yes this provides little value
#PredAll %>% ggplot(aes(x = Value, y = ActualValue, fill = Model)) + geom_point(aes(color = Model)) + geom_smooth(formula = y~x)+
#facet_wrap(facets = PredAll$Model) + ggtitle("Scatter Plot of Models") + xlab("Predicted") + ylab("Observed")

# Column
linearRmsedf %>% group_by(variable) %>% summarise(mean = (mean(value))) %>% 
  ggplot(aes(x = reorder(variable, -mean), y = mean, fill = variable)) + geom_col(width = 0.75) + geom_text(aes(label = round(mean,3), vjust = -0.5)) + 
  ggtitle("Average RMSE over 500 Shuffles (Linear Models)") + xlab("Model #") + ylab("Mean RMSE")

# Boxplot
linearRmsedf %>%  ggplot(aes(x = variable, y = value)) + geom_boxplot(aes(fill = variable)) + facet_wrap(~variable,ncol = TRUE) +
  ggtitle("Mean RMSE Distribution by Model") + ylab("Mean RMSE") + coord_flip() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())

# Histogram
linearRmsedf %>%  ggplot(aes(x = value)) + geom_histogram(aes(fill = variable)) + facet_wrap(~variable,ncol = TRUE) +
  ggtitle("Mean RMSE Distribution by Model") + xlab("Mean RMSE") + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())

# t-test or one way ANOVA to see if our errors are significantly different
t.test(LModelRMSE1,LModelRMSE2, var.equal = FALSE)

```

```{r}
# So it turns out that KNN imputing is done in a waaay different manner - may not need this piece at all ----
# This is up and running. Need to find optimal k and add scaled variables for better analysis. Currently predicting right with LM
iterations = 50
RMSE.KNN1.AGG = c()

for(i in 1:iterations)
{
  #set.seed(i)
  index<- sample(1:dim(BeerBreweryNA.delete)[1],round(splitperc*dim(BeerBreweryNA.delete)[1]),replace=F)
  train<- BeerBreweryNA.delete[index,]
  test<- BeerBreweryNA.delete[-index,]
  KNN.Model1 <- knn.reg(as.data.frame(train[,4]), as.data.frame(test[,4]), train$IBU, k=5)
  KNN.Predictions1 = as.data.frame(KNN.Model1$pred)
  names(KNN.Predictions1)[1] <- "Predictions"
  
  PredvActual <- data.frame(Predictions = c(KNN.Predictions1), Actual = c(test$IBU))
  PredvActual = PredvActual %>% mutate(ResidSquError1 = (Predictions - Actual)^2)

  RMSE.KNN1 = sqrt(mean(PredvActual$ResidSquError1))
  #print(RMSE.KNN1)
  RMSE.KNN1.AGG = c(RMSE.KNN1.AGG, RMSE.KNN1)

}
RMSE.KNN1.AGG = as.data.frame(RMSE.KNN1.AGG)
mean(RMSE.KNN1.AGG$RMSE.KNN1.AGG)
```

```{r}
# Linear Model Imputation Method (q3) ----
# Uses linear model 1 to predict IBU from ABV, Also removes the 17 ABV NAs that are left
# This predicts right into BeerBrewery we may need to offload these into a second data set depending on analysis needs.
BeerBreweryLMPredicted <- BeerBrewery %>% filter((!is.na(BeerBrewery$ABV))) %>% 
  mutate(Prediction = predict(linearmodel2, .)) %>% mutate(IBU = ifelse(is.na(IBU), Prediction, IBU))

```

```{r, warning = FALSE}
# IBU Distribution Characteristics - Summary Stats and distribution of IBU After LM impute (q3) ----
g1 = BeerBrewery %>% na.omit() %>% ggplot(aes(x = IBU)) + geom_histogram(binwidth = 2) + xlim(0,150) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank())

g2 = BeerBrewery %>% na.omit()  %>% ggplot(aes(x = IBU)) + geom_boxplot() + xlim(0,150) + 
  theme(axis.ticks.y = element_blank())

g3 = BeerBrewery %>% na.omit() %>% ggplot(aes(sample = IBU)) + stat_qq_line() + stat_qq() + ylim(0,150) + xlab("Quantile") + ylab("IBU")

g4 = ggdraw() + draw_label("Distribution Characteristics \nof LM Imputed IBU", color = "Gray2", size = 20)

plot_grid(g1,g3,g2,g4, ncol = 2)
```

```{r}
# KNN Imputation Method (q3) ----
# this method cant have both columns of the variables be NA - so this drops the 17 NA ABV values total 2393 instead 2410....
# This is pretty cool it imputes the values directly into the columns so we just have to unscale what we need
BeerBrewery1 = BeerBrewery %>% filter((!is.na(BeerBrewery$ABV)))
BeerBreweryKNNPredicted <- preProcess(BeerBrewery1[,4:5], method = "knnImpute", k = 20)
BeerBreweryKNNPredicted <- predict(BeerBreweryKNNPredicted, BeerBrewery1)

# Unscales the IBU So we can analyze it
BeerBreweryKNNPredicted = BeerBreweryKNNPredicted %>% mutate(IBUPred = (IBU*sd(BeerBrewery1$IBU, na.rm = TRUE) + mean(BeerBrewery1$IBU, na.rm = TRUE)))
```

```{r, warning=FALSE}
# IBU Distribution Characteristics - Summary Stats and distribution of IBU After KNN impute (q3) ----
g1 = BeerBrewery %>% na.omit() %>% ggplot(aes(x = IBU)) + geom_histogram(binwidth = 2) + xlim(0,150) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank())

g2 = BeerBrewery %>% na.omit()  %>% ggplot(aes(x = IBU)) + geom_boxplot() + xlim(0,150) + 
  theme(axis.ticks.y = element_blank())

g3 = BeerBrewery %>% na.omit() %>% ggplot(aes(sample = IBU)) + stat_qq_line() + stat_qq() + ylim(0,150) + xlab("Quantile") + ylab("IBU")

g4 = ggdraw() + draw_label("Distribution Characteristics \nof KNN Imputed IBU", color = "Gray2", size = 20)

plot_grid(g1,g3,g2,g4, ncol = 2)
```

```{r, warning=FALSE}
# Comparing distributions of Imputed IBUs with observed data (q3) ----
g1 = BeerBreweryLMPredicted %>% ggplot(aes(x = IBU)) + geom_histogram(binwidth = 3)
g2 = BeerBreweryKNNPredicted %>% ggplot(aes(x = IBUPred)) + geom_histogram(binwidth = 3)
g3 = BeerBreweryNA.delete %>% ggplot(aes(x = IBU)) + geom_histogram(binwidth = 3)

f1 = BeerBreweryLMPredicted %>% ggplot(aes(x = IBU)) + geom_boxplot()
f2 = BeerBreweryKNNPredicted %>% ggplot(aes(x = IBUPred)) + geom_boxplot()
f3 = BeerBreweryNA.delete %>% ggplot(aes(x = IBU)) + geom_boxplot()

plot_grid(g1, g2, g3,f1,f2,f3, labels = c("LM","KNN", "OBS"), ncol = 3, nrow = 2)
```

```{r}
# part of question 3 analysis LM Predictions v KNN Predictions ----
# Looking at how different the predictions are - not very different so could use either one. 
LMPred = BeerBreweryLMPredicted %>% dplyr::select(Prediction)
KNNPred = BeerBreweryKNNPredicted %>% dplyr::select(IBUPred)
difference = cbind(LMPred, KNNPred)
difference = difference %>% mutate(Pred.Diff = (Prediction - IBUPred))
t.test(difference$Prediction, difference$IBUPred, var.equal = FALSE)

difference %>% ggplot(aes(x = IBUPred, y = Prediction)) + geom_point() + geom_smooth() + geom_jitter() + 
  xlab("KNN Predicted IBU") + ylab("LM Predicted IBU") + ggtitle("LM v KNN Predicted IBU")
```

```{r, warning=FALSE}
# Answer Project question #4 Median ABV by State ----
# Top 15
BeerBreweryLMPredicted %>% group_by(State) %>% na.omit() %>% summarise(StateMedian = median(ABV)) %>% arrange(-StateMedian) %>% slice(1:15) %>%
  ggplot(aes(x = reorder(State, -StateMedian), y = StateMedian)) + geom_col() +
  theme(axis.text.x = element_text(angle = 90, vjust = -0.05)) +  xlab("State") + ylab('Median') + 
  ggtitle("Median ABV By State (Highest)") + geom_text(aes(label = StateMedian), vjust = -0.5, size = 3)

# Map Graphic
mapBreweries = BeerBreweryLMPredicted %>% na.omit() %>% group_by(State) %>% summarise(StateMedian = median(ABV))
mapBreweries$State = as.character(mapBreweries$State)
mapBreweries$State = sub(" ", "", mapBreweries$State)
map2 = merge(statepop, mapBreweries, by.x = "abbr", by.y = "State")
plot_usmap(data = map2, values = "StateMedian", color = "red", labels = TRUE, label_color = "white") + 
  scale_fill_continuous(name = "Brewery count", label = scales::comma) + 
  labs(title = "USA MAP", subtitle="Median ABV by State") +
  theme(legend.position = "right")

BeerBreweryLMPredicted %>% group_by(State) %>% na.omit() %>% summarise(StateMedian = median(ABV)) %>% arrange(StateMedian) %>% slice(1:15) %>%
  ggplot(aes(x = reorder(State, -StateMedian), y = StateMedian)) + geom_col() +
  theme(axis.text.x = element_text(angle = 90, vjust = -0.05)) +  xlab("State") + ylab('Median') + 
  ggtitle("Median ABV By State (Lowest)") + geom_text(aes(label = StateMedian), vjust = -0.5, size = 3)
```

```{r, warning=FALSE}
# Answer Project question #4 Median IBU Content by State ----
BeerBreweryLMPredicted %>% group_by(State) %>% na.omit() %>% summarise(StateMedian = round(median(IBU),3)) %>% arrange(-StateMedian) %>% slice(1:15) %>%
  ggplot(aes(x = reorder(State, -StateMedian), y = StateMedian)) + geom_col() +
  theme(axis.text.x = element_text(angle = 90, vjust = -0.05)) +  xlab("State") + ylab('Median') + 
  ggtitle("Median IBU By State (Highest)") + geom_text(aes(label = StateMedian), vjust = -0.5, size = 3)

mapBreweries = BeerBreweryLMPredicted %>% na.omit() %>% group_by(State) %>% summarise(StateMedian = median(IBU))
mapBreweries$State = as.character(mapBreweries$State)
mapBreweries$State = sub(" ", "", mapBreweries$State)
map2 = merge(statepop, mapBreweries, by.x = "abbr", by.y = "State")
plot_usmap(data = map2, values = "StateMedian", color = "red", labels = TRUE, label_color = "white") + 
  scale_fill_continuous(name = "Brewery count", label = scales::comma) + 
  labs(title = "USA MAP", subtitle="Median IBU by State") +
  theme(legend.position = "right")
```


```{r}
# question 8 - Creates new data set and runs classification on a 70/30 CV ----
BeerBreweryLMPredicted = BeerBreweryLMPredicted %>% mutate(StyleChar = as.character(Style))
IPA = BeerBreweryLMPredicted %>% filter(str_detect(StyleChar,"IPA"))
Ale = BeerBreweryLMPredicted %>% filter(str_detect(StyleChar,"Ale")) %>% filter(!str_detect(StyleChar,"India Pale Ale"))
AleIPA = Ale %>% filter(str_detect(StyleChar,"IPA"))

IPA = IPA %>% mutate(IPAorAle = "IPA") 
Ale = Ale %>% mutate(IPAorAle = "Ale")

Bud = rbind(IPA,Ale)
Bud$IPAorAle = as.factor(Bud$IPAorAle)

splitperc = 0.70
set.seed(4)
index<- sample(1:dim(Bud)[1],round(splitperc*dim(Bud)[1]),replace=F)
  train<- Bud[index,]
  test<- Bud[-index,]

classifications = knn(train[,4:5],test[,4:5],train$IPAorAle, prob = TRUE, k = 3)
table(classifications,test$IPAorAle)
confusionMatrix(table(classifications,test$IPAorAle))
```


```{r}
# project number 5 ----
# Max ABV and IBU drawn from Linear predicted data
sprintf("The Max ABV is %s, from the beer %s,in%s",
        BeerBreweryLMPredicted$ABV[which.max(BeerBreweryLMPredicted$ABV)],
        BeerBreweryLMPredicted$Beer[which.max(BeerBreweryLMPredicted$ABV)],
        BeerBreweryLMPredicted$State[which.max(BeerBreweryLMPredicted$ABV)])

sprintf("The Max IBU is %s, from the beer %s,in%s",
        BeerBreweryLMPredicted$IBU[which.max(BeerBreweryLMPredicted$IBU)],
        BeerBreweryLMPredicted$Beer[which.max(BeerBreweryLMPredicted$IBU)],
        BeerBreweryLMPredicted$State[which.max(BeerBreweryLMPredicted$IBU)])
```














